Summary of the things that I learned

### 2024-10-08 400-algebraic-structures.tex
Address a lot of feedback, do a spellcheck

\begin{remark}[\coqident{AlgebraicTheories.AlgebraicTheoryCategory}{limits_algebraic_theory_cat}]\label{rem:algebraic-theory-limits}
  We can construct binary products of algebraic theories, with sets $ (T \times T^\prime)_n = T_n \times T^\prime_n $, variables $ (x_i, x_i) $ and substitution
  \[ (f, f^\prime) \bullet (g, g^\prime) = (f \bullet g, f^\prime \bullet g^\prime). \]
  In the same way, the category of algebraic theories has all limits.
\end{remark}

@@

\begin{remark}
  The category of algebras has all limits. The set of a limit of algebras is the limit of the underlying sets.
\end{remark}

@@

\begin{remark}[\coqident{AlgebraicTheories.PresheafCategory}{limits_presheaf_cat}]
  The category of presheaves has all limits. The $ n $th set $ \overline{P}_n $ of a limit $ \overline{P} $ of presheaves $ P_i $ is the limit of the $ n $th sets $ P_{i, n} $ of the presheaves in the limit diagram.
\end{remark}

@@

\begin{definition}[\coqident{AlgebraicTheories.LambdaTheories}{has_β}]
  We say that a $ \lambda $-theory $ L $ satisfies $ \beta $-equality (or that it is a $ \lambda $-theory with $ \beta $) if $ \rho_n \circ \lambda_n = \id{L_n} $ for all $ n $. We say that is satisfies $ \eta $-equality if $ \lambda_n \circ \rho_n = \id{L_{n + 1}} $ for all $ n $.
\end{definition}

@@

\begin{remark}[\coqident{AlgebraicTheories.LambdaTheoryCategory}{limits_lambda_theory_cat}]
  The category of lambda theories has all limits, with the underlying algebraic theory of a limit being the limit of the underlying algebraic theories.
\end{remark}

@@

\begin{remark}[\coqident{AlgebraicTheories.LambdaTheories}{beta_equality}]
  Note that if $ L $ has $ \beta $-equality, we have
  \[ \lambda(f) g = \rho(\lambda(f)) \bullet (x_1, \dots, x_n, g) = f \bullet (x_1, \dots, x_n, g), \]
  so we have the usual $ \beta $-equality. In the same way $ \eta $-equality of $ L $ gives
  \[ \lambda(\iota_{n, 1}(f) x_{n + 1}) = \lambda(\rho(f)) = f. \]
\end{remark}
\begin{remark}[\coqident{AlgebraicTheories.LambdaTheories}{app_from_app'}]
  Also note that for $ f: L_n $,
  \[ \rho(f) = \rho(x_1 \bullet f) = \iota_{n, 1}(f) x_{n + 1}. \]
  Therefore, we can also think of the application as being the primary operation, from which we derive $ \rho $. In the same way, we have
  \[ \rho^m(f) = \iota_{n, m}(f) x_{n + 1} \dots x_{n + m}. \]
\end{remark}
\begin{remark}[\coqident{AlgebraicTheories.LambdaTheories}{app}]
  Note that for $ f, g : L_n $,
  \[
    \rho(f) \bullet (x_1, \dots, x_n, g)
    = \rho(x_1) \bullet (\iota_{n, 1}(f), x_{n + 1}) \bullet (x_1, \dots, x_n, g)
    = \rho(x_1) \bullet (\iota_{n, 1}(f), g),
  \]
  so we could also define the application as $ f g = \rho(f) \bullet (x_1, \dots, x_n, g) $, although that is more complicated.
\end{remark}

@@

\begin{remark}
  Another counterexample is the category $ \mathbf{Top} $ of topological spaces. We have a forgetful functor $ G: \mathbf{Top} \to \SET $ that just forgets the topology. On the other hand, we have a free functor $ F: \SET \to \mathbf{Top} $ which endows a set with the discrete topology. The construction above yields the inital algebraic theory $ T_n = \{ 1, \dots, n \} $, with an algebra action on every topological space $ i \bullet (a_1, \dots, a_n) = a_i $. Now, note that we can endow the set $ \{ \top, \bot \} $ with four different, nonisomorphic topologies, which all yield the same $ T $-algebra. In other words: the $ T $-algebra structure does not preserve the topological information. Therefore, the functor $ \alpha: \mathbf{Top} \to \Alg T $ is not an equivalence.
\end{remark}

@@

\begin{remark}[\coqident{AlgebraicTheories.Examples.TheoryAlgebra}{theory_algebra_free}]
  Recall from \ref{lem:lawvere-algebra} that $ T $-algebras are equivalent to finite-product-preserving $ \SET $-valued functors on the Lawvere theory $ \mathbf L $ associated to $ T $. Now, recall from Definition \ref{def:Yoneda-embedding} that we can embed any category $ C $ as $ \op C $ inside its category of $ \SET $-valued functors. This embeds $ n: \mathbf L $ as the theory algebra $ T_n $. Then the Yoneda Lemma gives a bijection
  \[ \Alg T(T_n, A) \cong A^n = \SET(\{ 1, \dots, n \}, A) \]
  natural in $ n $ and $ A $. Explicitly, it sends $ f: \Alg T(T_n, A) $ to $ (f(x_i))_i $ and $ (a_i)_i : A^n $ to $ f \mapsto f \bullet a $. The natural equivalence immediately shows that $ T_n $ is the free $ T $-algebra on $ n $ elements.
\end{remark}

@@

\begin{remark}[\coqident{AlgebraicTheories.RepresentationTheorem}{presheaf_to_L}]\label{rem:presheaf-Yoneda}
  Recall from \ref{lem:lawvere-presheaf} that $ T $-presheaves are equivalent to presheaves on the Lawvere theory $ \mathbf L $ associated to $ T $. Now, recall from Definition \ref{def:Yoneda-embedding} that we can embed any category inside its own category of presheaves. This embeds $ n: \mathbf L $ as the power $ T^n = (T_m^n)_m $ of the theory presheaf. Then the Yoneda Lemma gives a bijection
  \[ \Pshf T(T^n, Q) \cong Q_n \]
  natural in $ n $ and $ Q $. Explicitly, it sends $ f: \Pshf T(T^n, Q) $ to $ f_n(x_1, \dots, x_n) $ and $ q: Q_n $ to $ (t_i)_i \mapsto q \bullet t $.
\end{remark}

>>>>

\begin{lemma}[\coqident{AlgebraicTheories.AlgebraicTheoryCategory}{limits_algebraic_theory_cat}]\label{rem:algebraic-theory-limits}
  We can construct binary products of algebraic theories, with sets $ (T \times T^\prime)_n = T_n \times T^\prime_n $, variables $ (x_i, x_i) $ and substitution
  \[ (f, f^\prime) \bullet (g, g^\prime) = (f \bullet g, f^\prime \bullet g^\prime). \]
  In the same way, the category of algebraic theories has all limits.

  Note that the forgetful functor $ F: \AlgTh \to \SET^{\mathbb N} $ creates limits, since any diagram $ d $ has a limit and the underlying set of the limit of $ d $ is the limit of the underlying sets of the objects in $ d $.
\end{lemma}

\begin{lemma}[\coqident{AlgebraicTheories.AlgebraicTheoryCategory}{is_univalent_algebraic_theory_cat}]
  Since an isomorphism of algebraic theories $ S \simeq T $ consists of pointwise isomorphisms $ f_n: S_n \simeq T_n $ that respect the variables and substitution, the category of algebraic theories is univalent.
\end{lemma}

@@

\begin{remark}
  The category of algebras has all limits. The set of a limit of algebras is the limit of the underlying sets, so the forgetful functor to the category of sets creates limits.
\end{remark}

\begin{lemma}[\coqident{AlgebraicTheories.AlgebraCategory}{is_univalent_algebra_cat}]
  Note that just like with algebraic theories, the category of $ T $-algebras is univalent because its (iso)morphisms preserve $ \bullet $.
\end{lemma}

@@

\begin{lemma}[\coqident{AlgebraicTheories.PresheafCategory}{limits_presheaf_cat}]
  The category of presheaves has all limits. The $ n $th set $ \overline{P}_n $ of a limit $ \overline{P} $ of presheaves $ P_i $ is the limit of the $ n $th sets $ P_{i, n} $ of the presheaves in the limit diagram. So just like with algebraic theories and algebras, the forgetful functor from the category of presheaves to the category of indexed sets creates limits.
\end{lemma}

\begin{lemma}[\coqident{AlgebraicTheories.AlgebraCategory}{is_univalent_algebra_cat}]
  Note that just like with algebraic theories and algebras, the category of $ T $-presheaves is univalent because its (iso)morphisms preserve $ \bullet $.
\end{lemma}

@@

\begin{definition}[\coqident{AlgebraicTheories.LambdaTheories}{has_β} \coqident{AlgebraicTheories.LambdaTheories}{has_η}]\label{def:beta-equality}
  We say that a $ \lambda $-theory $ L $ satisfies $ \beta $-equality (or that it is a $ \lambda $-theory with $ \beta $) if $ \rho_n \circ \lambda_n = \id{L_n} $ for all $ n $. We say that is satisfies $ \eta $-equality if $ \lambda_n \circ \rho_n = \id{L_{n + 1}} $ for all $ n $.
\end{definition}

@@

\begin{lemma}[\coqident{AlgebraicTheories.LambdaTheoryCategory}{limits_lambda_theory_cat}]
  The category of lambda theories has all limits, with the underlying algebraic theory of a limit being the limit of the underlying algebraic theories. Therefore, the forgetful functor to the category of algebraic theories creates limits.
\end{lemma}

\begin{lemma}[\coqident{AlgebraicTheories.LambdaTheoryCategory}{is_univalent_lambda_theory_cat}]
  Note that just like with algebraic theories, the category of $ \lambda $-theories is univalent because its (iso)morphisms preserve $ \rho $ and $ \lambda $.
\end{lemma}

@@

\begin{lemma}[\coqident{AlgebraicTheories.LambdaTheories}{beta_equality}]
  The definitions for $ \beta $- and $ \eta $-equality in Definition \ref{def:beta-equality} correspond to the usual notions.
\end{lemma}
\begin{proof}
  If $ L $ has $ \beta $-equality, we have
  \[ \lambda(f) g = \rho(\lambda(f)) \bullet (x_1, \dots, x_n, g) = f \bullet (x_1, \dots, x_n, g), \]
  so we have the usual $ \beta $-equality. In the same way $ \eta $-equality of $ L $ gives
  \[ \lambda(\iota_{n, 1}(f) x_{n + 1}) = \lambda(\rho(f)) = f. \]
\end{proof}

\begin{remark}[\coqident{AlgebraicTheories.LambdaTheories}{app_from_app'}]
  Also note that for $ f: L_n $,
  \[ \rho(f) = \rho(x_1 \bullet f) = \iota_{n, 1}(f) x_{n + 1}. \]
  Therefore, we can also think of the application as being the primary operation, from which we derive $ \rho $. In the same way, we have
  \[ \rho^m(f) = \iota_{n, m}(f) x_{n + 1} \dots x_{n + m}. \]
\end{remark}

\begin{remark}[\coqident{AlgebraicTheories.LambdaTheories}{app}]
  Note that for $ f, g : L_n $,
  \[
    \rho(f) \bullet (x_1, \dots, x_n, g)
    = \rho(x_1) \bullet (\iota_{n, 1}(f), x_{n + 1}) \bullet (x_1, \dots, x_n, g)
    = \rho(x_1) \bullet (\iota_{n, 1}(f), g),
  \]
  so we could also define the application as $ f g = \rho(f) \bullet (x_1, \dots, x_n, g) $, although that is more complicated.
\end{remark}

@@

\begin{remark}
  Another counterexample is the category $ \mathbf{Top} $ of topological spaces. We have a forgetful functor $ G: \mathbf{Top} \to \SET $ that just forgets the topology. On the other hand, we have a free functor $ F: \SET \to \mathbf{Top} $ which endows a set with the discrete topology. The construction above yields the initial algebraic theory $ T_n = \{ 1, \dots, n \} $, with an algebra action on every topological space $ i \bullet (a_1, \dots, a_n) = a_i $. Now, note that we can endow the set $ \{ \top, \bot \} $ with four different, nonisomorphic topologies, which all yield the same $ T $-algebra. In other words: the $ T $-algebra structure does not preserve the topological information. Therefore, the functor $ \alpha: \mathbf{Top} \to \Alg T $ is not an equivalence.
\end{remark}

@@

\begin{lemma}[\coqident{AlgebraicTheories.Examples.TheoryAlgebra}{theory_algebra_free}]
  $ T_n $ is the free $ T $-algebra on $ n $ generators.
\end{lemma}
\begin{proof}
  Recall from Lemma \ref{lem:lawvere-algebra} that $ T $-algebras are equivalent to finite-product-preserving $ \SET $-valued functors on the Lawvere theory $ \mathbf L $ associated to $ T $. Now, recall from Definition \ref{def:Yoneda-embedding} for any category $ C $, we can embed $ \op C $ inside $ [C, \SET] $, the category of $ \SET $-valued functors on $ C $. This embeds $ n: \mathbf L $ as the theory algebra $ T_n $. Then the Yoneda Lemma gives a bijection
  \[ \Alg T(T_n, A) \cong A^n = \SET(\{ 1, \dots, n \}, A) \]
  natural in $ n $ and $ A $. Explicitly, it sends $ f: \Alg T(T_n, A) $ to $ (f(x_i))_i $ and $ (a_i)_i : A^n $ to $ f \mapsto f \bullet a $. The natural equivalence immediately shows that $ T_n $ is the free $ T $-algebra on $ n $ elements.
\end{proof}

@@

\begin{lemma}[\coqident{AlgebraicTheories.RepresentationTheorem}{presheaf_to_L}]\label{rem:presheaf-Yoneda}
  We have natural bijections
  \[ \Pshf T(T^n, Q) \cong Q_n \]
  for $ Q : \Pshf T $.
\end{lemma}
\begin{proof}
  Recall from Lemma \ref{lem:lawvere-presheaf} that $ T $-presheaves are equivalent to presheaves on the Lawvere theory $ \mathbf L $ associated to $ T $. Now, recall from Definition \ref{def:Yoneda-embedding} that we can embed any category inside its own category of presheaves. This embeds $ n: \mathbf L $ as the power $ T^n = (T_m^n)_m $ of the theory presheaf. Then the Yoneda Lemma gives a bijection
  \[ \Pshf T(T^n, Q) \cong Q_n \]
  natural in $ n $ and $ Q $. Explicitly, it sends $ f: \Pshf T(T^n, Q) $ to $ f_n(x_1, \dots, x_n) $ and $ q: Q_n $ to $ (t_i)_i \mapsto q \bullet t $.
\end{proof}

### 2024-10-08 500-previous-work.tex
Address a lot of feedback, do a spellcheck

Later on, we will need not only pairs and their projects, but also $ n $-tuples with projections. Therefore, we define
\begin{align*}
  (a_i)_i = (a_1, \dots, a_n) &= ((\dots((c, a_1), a_2), \dots), a_n);\\
  \langle a_i \rangle_i = \langle a_1, \dots, a_n \rangle &= \langle\langle\dots\langle\langle c, a_1\rangle, a_2\rangle, \dots\rangle, a_n\rangle;\\
  \pi_{n, i} &= \pi_2 \circ \underbrace{\pi_1 \circ \dots \circ \pi_1}_{n - i}
\end{align*}
for some constant $ c $, which usually is someting like $ \lambda x_{n + 1}, x_{n + 1} $.

\begin{definition}[\coqident{AlgebraicTheories.CategoryOfRetracts}{R}]
  We define the category \index{R}$ \R $ as the Karoubi envelope $ \overline C_{L_0} $ of the one-point category based on the monoid of the $ \lambda $-terms without free variables under composition. In this case, we choose to interpret the Karoubi envelope as the very syntactical construction using idempotents, because Scott reasons about them in this way:
  \[ \R_0 = \{ A : L_0 \mid A \circ A = A \} \quad \text{and} \quad \R(A, B) = \{ f: L_0 \mid B \circ f \circ A = f \}, \]
  with $ \id A = A $ and composition given by $ \circ $.
\end{definition}

@@

  On the other hand, for an \textit{untyped} $ \lambda $-calculus, we need a cartesian closed category with a `reflexive object'. This is because in the untyped $ \lambda $-calculus, we can apply arbitrary terms to each other. For example, we can apply the term $ (\lambda x_1, x_1 x_1) $ to itself, which would not be typable in the simply typed $ \lambda $-calculus. Suppose that we have a category $ C $ and an object $ U $ such that the morphisms $ C(U^n, U) $ give the untype $ \lambda $-terms in $ n $ free variables, for all $ n $. Now, given two terms $ f, g : C(U^n, U) $, for the application $ f g $, we need to consider $ f $ as a morphism in $ C(U^n, U^U) $. We can do this by postcomposing with a morphism $ \varphi: C(U, U^U) $. On the other hand, if $ n > 0 $, then $ (\lambda x_n, f) $ is a morphism in $ C(U^{n - 1}, U^U) $, but it is a term in $ n - 1 $ free variables, so it should be in $ C(U^{n - 1}, U) $. For this, we postcompose with a morphism $ \psi: C(U^U, U) $. Now, for our untyped $ \lambda $-calculus to have $ \beta $-equality, we need $ \psi \cdot \varphi = \id{U^U} $, which means that the exponential $ U^U $ of $ U $ is a retract of $ U $. This is exactly what it means for $ U $ to be a \iindex{reflexive object}: an object $ U $ in a cartesian closed category, that has a retraction onto its `function space' $ U^U $. Note that if we want our $ \lambda $-theory to also have $ \eta $-equality, the retraction must be an isomorphism.

@@

Now, analogously to \ref{lem:locally-cartesian-closed}, Taylor shows:
\begin{lemma}
  If a category $ C $ is cartesian closed relative to a class of display maps $ D $, then the fiber categories $ (C \downarrow_D A) $ are cartesian closed and the substitution functors $ \alpha^* $ preserve this structure.
\end{lemma}
\begin{proof}
  Taylor proves this in a series of lemmas leading up to \S 4.3.7 in \autocite{taylor}. It is also proved as Proposition 6 of \autocite{theory-of-constructions}.
\end{proof}

@@

Now, it is not hard to show that Hyland's and Selinger's notions of $ \lambda $-theory are equivalent: If we have one of Selinger's $ \lambda $-theories with a countable set of variables, enumerate the variables as $ x_1, x_2, \dots $ and let $ L_n $ be the set of terms with only the free variables $ x_1, \dots, x_n $. Then, if we quotient by the equivalence relation, we get one of Hyland's $ \lambda $-theories. Conversely, if we start with one of Hyland's $ \lambda $-theories $ L $, we can consider $ L_n $ as a subset of $ L_{n + 1} $ by sending $ x_{n, i} $ to $ x_{n + 1, i} $. If we take the union $ \bar L = \bigcup_n L_n $ (officially, this is a directed limit), we have a function $ f: \Lambda_{\bar L} \to \bar L $, because the constants of $ \Lambda_{\bar L} $ are exactly the terms of $ \bar L $ and because $ \lambda $-theories in Hyland's sense support the operations of the $ \lambda $-calculus (see subsection \ref{subsec:lambda-calculus-operations}). This gives an equivalence relation on $ \Lambda_{\bar L} $ by taking $ a\ `='\ b $ if $ f(a) = f(b) $.

>>>>

Later on, we will need not only pairs and their projects, but also $ n $-tuples with projections. Therefore, we define
\begin{align*}
  (a_i)_i = (a_1, \dots, a_n) &= ((\dots((c, a_1), a_2), \dots), a_n);\\
  \langle a_i \rangle_i = \langle a_1, \dots, a_n \rangle &= \langle\langle\dots\langle\langle c, a_1\rangle, a_2\rangle, \dots\rangle, a_n\rangle;\\
  \pi_{n, i} &= \pi_2 \circ \underbrace{\pi_1 \circ \dots \circ \pi_1}_{n - i}
\end{align*}
for some constant $ c $, which usually is something like $ \lambda x_{n + 1}, x_{n + 1} $.

Recall from Section \ref{sec:monoid-category} that we can view any monoid $ M $ as a one-object category $ C_M $, where the morphisms are the elements of $ M $.

\begin{definition}[\coqident{AlgebraicTheories.CategoryOfRetracts}{R}]
  Note that the set of $ \lambda $-terms without free variables $ L_0 $ has a monoid structure under the composition defined above. The category \index{R}$ \R $ is defined as the Karoubi envelope $ \overline C_{L_0} $ of the category $ C_{L_0} $ of this monoid.

  We choose to implement the Karoubi envelope using a slightly different (but equivalent) very syntactical construction using idempotents, because Scott reasons about them in this way:
  \[ \R_0 = \{ A : L_0 \mid A \circ A = A \} \quad \text{and} \quad \R(A, B) = \{ f: L_0 \mid B \circ f \circ A = f \}, \]
  with $ \id A = A $ and composition given by $ \circ $.
\end{definition}

@@

  On the other hand, for an \textit{untyped} $ \lambda $-calculus, we need a cartesian closed category with a `reflexive object'. This is because in the untyped $ \lambda $-calculus, we can apply arbitrary terms to each other. For example, we can apply the term $ (\lambda x_1, x_1 x_1) $ to itself, which would not be typable in the simply typed $ \lambda $-calculus. Suppose that we have a category $ C $ and an object $ U $ such that the morphisms $ C(U^n, U) $ give the untyped $ \lambda $-terms in $ n $ free variables, for all $ n $. Now, given two terms $ f, g : C(U^n, U) $, for the application $ f g $, we need to consider $ f $ as a morphism in $ C(U^n, U^U) $. We can do this by postcomposing with a morphism $ \varphi: C(U, U^U) $. On the other hand, if $ n > 0 $, then $ (\lambda x_n, f) $ is a morphism in $ C(U^{n - 1}, U^U) $, but it is a term in $ n - 1 $ free variables, so it should be in $ C(U^{n - 1}, U) $. For this, we postcompose with a morphism $ \psi: C(U^U, U) $. Now, for our untyped $ \lambda $-calculus to have $ \beta $-equality, we need $ \psi \cdot \varphi = \id{U^U} $, which means that the exponential $ U^U $ of $ U $ is a retract of $ U $. This is exactly what it means for $ U $ to be a \iindex{reflexive object}: an object $ U $ in a cartesian closed category, that has a retraction onto its `function space' $ U^U $. Note that if we want our $ \lambda $-theory to also have $ \eta $-equality, the retraction must be an isomorphism.

@@

Now, analogously to Lemma \ref{lem:locally-cartesian-closed}, Taylor shows:
\begin{lemma}
  If a category $ C $ is cartesian closed relative to a class of display maps $ D $, then the fiber categories $ (C \downarrow_D A) $ are cartesian closed and the substitution functors $ \alpha^* $ preserve this structure.
\end{lemma}
\begin{proof}
  Taylor proves this in a series of lemmas leading up to \S 4.3.7 in \autocite{taylor}. It is also proved as Proposition 6 of \autocite{theory-of-constructions}.
\end{proof}

@@

Now, it is not hard to show that Hyland's and Selinger's notions of $ \lambda $-theory are equivalent: If we have one of Selinger's $ \lambda $-theories with a countable set of variables, enumerate the variables as $ x_1, x_2, \dots $ and let $ L_n $ be the set of terms with only the free variables $ x_1, \dots, x_n $. Then, if we quotient by the equivalence relation, we get one of Hyland's $ \lambda $-theories. Conversely, if we start with one of Hyland's $ \lambda $-theories $ L $, we can consider $ L_n $ as a subset of $ L_{n + 1} $ by sending $ x_{n, i} $ to $ x_{n + 1, i} $. If we take the union $ \bar L = \bigcup_n L_n $ (officially, this is a directed limit), we have a function $ f: \Lambda_{\bar L} \to \bar L $, because the constants of $ \Lambda_{\bar L} $ are exactly the terms of $ \bar L $ and because $ \lambda $-theories in Hyland's sense support the operations of the $ \lambda $-calculus (see Subsection \ref{subsec:lambda-calculus-operations}). This gives an equivalence relation on $ \Lambda_{\bar L} $ by taking $ a\ `='\ b $ if $ f(a) = f(b) $.

### 2024-10-08 600-paper.tex
Address a lot of feedback, do a spellcheck

The $ \Lambda $-algebra structure gives the terms of $ A $ quite a lot of interesting behaviour. For example, we can define `function application' and composition as
\[ a b = (x_1 x_2) \bullet (a, b) \quad \text{and} \quad a \circ b = (x_1 \circ x_2) \bullet (a, b), \]
and the same for the other constructions at the start of Section \ref{sec:retracts-category}.

@@

\begin{remark}\label{rem:ract-presheaf-equivalence}
  Note that, like in the last chapter, $ \R_A $ pops up as the Karoubi envelope of the monoid category $ C_{A_1} $, and fits into the following diagram:
  \begin{center}
    \begin{tikzcd}
      & C_{A_1} \arrow[d, hookrightarrow, "\yo"] \arrow[r, hookrightarrow, "\iota_{C_{A_1}}"] & \R_A \arrow[d, hookrightarrow, "\yo"]\\
      \RAct{A_1} & P C_{A_1} \arrow[l, "\sim"] & P \R_A \arrow[l, "\sim"]
    \end{tikzcd}
  \end{center}
  Explicitly, this gives the embedding $ \R_A(\mathbf 1_1, -): \R_A \hookrightarrow \RAct{A_1} $ given by
  \[ X \mapsto \R_A(\mathbf 1_1, X) = \{ x : A \mid X \circ x = x \}. \]
  Also, note that if $ A = L_0 $ for some $ \lambda $-theory $ L $, then the monoid $ A_1 $ is equivalent to the monoid $ L_1 $, and $ \R_A $ is equivalent to our familiar category of retracts $ \R $. Using \ref{lem:equivalent-presheaf-cats}, we have the following 2-commutative diagram:
  \begin{center}
    \begin{tikzcd}
      &
      C_{{L_0}_1} \arrow[dd, "\yo" description, hook] \arrow[rrr, "\iota_{C_{{L_0}_1}}" description, hook] \arrow[rd, "\sim" description, no head] & & & \R_{L_0} \arrow[dd, "\yo" description, hook] \arrow[rd, "\sim" description, no head] & & \\
      &
      & C_{L_1} \arrow[dd, "\yo" description, hook] \arrow[r, hook] & \mathbf L \arrow[rr, hook] \arrow[dd, "\yo" description, hook] & & \mathbf R \arrow[dd, "\yo" description, hook] \arrow[rdd, hook] & \\
      \RAct{{L_0}_1} &
      P C_{{L_0}_1} \arrow[l, "\sim"'] \arrow[rd, "\sim" description, no head] & & & P \R_{L_0} \arrow[lll, "\sim" description] \arrow[rd, "\sim" description, no head] & & \\
      &
      & P C_{L_1} & P \mathbf L \arrow[l, "\sim" description] & & P \R \arrow[ll, "\sim" description] & \Pshf L \arrow[lll, "\sim" description, bend left]
    \end{tikzcd}
  \end{center}
\end{remark}

@@

By Lemma 3.2 in \autocite{nlab:adjoint_equivalence} and Lemma \ref{lem:zigzag}, $ \eta $ and $ \epsilon $ satisfy both zigazg identities, and we can state the fundamental theorem of the $ \lambda $-calculus:
\begin{theorem}\label{thm:Hyland-fundamental-theorem}
  There is an adjoint equivalence $ \LamTh \cong \Alg{\Lambda} $, sending a $ \lambda $-theory $ L $ to the $ \Lambda $-algebra $ L_0 $, with an inverse functor that sends a $ \Lambda $-algebra $ A $ to the theory $ E_{\RAct{A_1}}(U_A) $.
\end{theorem}

>>>>

The $ \Lambda $-algebra structure gives the terms of $ A $ a lot of interesting behaviour. For example, we can define `function application' and composition as
\[ a b = (x_1 x_2) \bullet (a, b) \quad \text{and} \quad a \circ b = (x_1 \circ x_2) \bullet (a, b), \]
and the same for the other constructions at the start of Section \ref{sec:retracts-category}.

@@

\begin{remark}\label{rem:ract-presheaf-equivalence}
  Note that, like in the last chapter, $ \R_A $ pops up as the Karoubi envelope of the monoid category $ C_{A_1} $, and fits into the following diagram:
  \begin{center}
    \begin{tikzcd}
      & C_{A_1} \arrow[d, hookrightarrow, "\yo"] \arrow[r, hookrightarrow, "\iota_{C_{A_1}}"] & \R_A \arrow[d, hookrightarrow, "\yo"]\\
      \RAct{A_1} & P C_{A_1} \arrow[l, "\sim"] & P \R_A \arrow[l, "\sim"]
    \end{tikzcd}
  \end{center}
  Explicitly, this gives the embedding $ \R_A(\mathbf 1_1, -): \R_A \hookrightarrow \RAct{A_1} $ given by
  \[ X \mapsto \R_A(\mathbf 1_1, X) = \{ x : A \mid X \circ x = x \}. \]
  Also, note that if $ A = L_0 $ for some $ \lambda $-theory $ L $, then the monoid $ A_1 $ is equivalent to the monoid $ L_1 $, and $ \R_A $ is equivalent to our familiar category of retracts $ \R $. Using Lemma \ref{lem:equivalent-presheaf-cats}, we have the following 2-commutative diagram:
  \begin{center}
    \begin{tikzcd}
      &
      C_{{L_0}_1} \arrow[dd, "\yo" description, near start, hook] \arrow[rrr, "\iota_{C_{{L_0}_1}}" description, hook] \arrow[rd, "\sim" description, no head] & & & \R_{L_0} \arrow[dd, "\yo" description, near start, hook] \arrow[rd, "\sim" description, no head] & & \\
      &
      & C_{L_1} \arrow[dd, "\yo" description, near start, hook] \arrow[r, hook] & \mathbf L \arrow[rr, hook] \arrow[dd, "\yo" description, near start, hook] & & \mathbf R \arrow[dd, "\yo" description, near start, hook] \arrow[rdd, hook] & \\
      \RAct{{L_0}_1} &
      P C_{{L_0}_1} \arrow[l, "\sim"'] \arrow[rd, "\sim" description, no head] & & & P \R_{L_0} \arrow[lll, "\sim" description] \arrow[rd, "\sim" description, no head] & & \\
      &
      & P C_{L_1} & P \mathbf L \arrow[l, "\sim" description] & & P \R \arrow[ll, "\sim" description] & \Pshf L \arrow[lll, "\sim" description, bend left]
    \end{tikzcd}
  \end{center}
\end{remark}

@@

By Lemma 3.2 in \autocite{nlab:adjoint_equivalence} and Lemma \ref{lem:zigzag}, $ \eta $ and $ \epsilon $ satisfy both zigzag identities, and we can state the fundamental theorem of the $ \lambda $-calculus:
\begin{theorem}\label{thm:Hyland-fundamental-theorem}
  There is an adjoint equivalence $ \LamTh \cong \Alg{\Lambda} $, sending a $ \lambda $-theory $ L $ to the $ \Lambda $-algebra $ L_0 $, with an inverse functor that sends a $ \Lambda $-algebra $ A $ to the theory $ E_{\RAct{A_1}}(U_A) $.
\end{theorem}
